(Placeholder) Automatic selection of kinase expression constructs

### 2016-01-29 manuscript/ms.tex

{\color{blue} TODO}
For each target, the selected construct sequence was subcloned from the selected DNA plasmid.
Expression testing performed by QB3 MacroLab.

All genes were cloned into the 2BT10 plasmid, an AMP resistant ColE1 plasmid with a T7 promoter.
Each protein was tagged with a N-terminal His10-TEV and co-expressed with either YopH (for Tyr kinases) or lambda phosphatase (for Ser/Thr kinases). 
Single colonies of transformants were cultivated with 900 $\mu$L of MagicMedia into a gas permeable sealed 96-well block. 
The cultures were incubated at 37 C for 4 hours and then at 16 C for 40 hours while shacking. 
Next, cells were centrifuged and the pellets were frozen at -80 C overnight. 
Cells were lysed on a rotating platform at room temperature for an hour using 700 $\mu$L of Solulyse (Genlantis) supplemented with 400 mM NaCl, 20 mM imidazole and protease inhibitors. 
For protein purification, 500 $\mu$L of the soluble lysate was added to a 25 $\mu$L Ni-NTA resin in a 96-well filter plate. 
Nickel Buffer A (25 mM HEPES pH 7.5, 5\% glycerol, 400 mM NaCl, 20 mM imidazole, 1 mM BME) was added and the plate was mixed for 30 minutes at room temperature. 
The resin was washed with 2 mL of Nickel Buffer A. 
Target proteins were eluted by a 2 hour incubation at room temperature with 10 $\mu$g of TEV protease in 80 $\mu$L of Nickel Buffer A.
A subsequent wash with 40 $\mu$L of Nickel Buffer A was performed to release more target protein. 
Nickel Buffer B (25 mM HEPES pH 7.5, 5\% glycerol, 400 mM NaCl, 400 mM imidazole, 1 mM BME) was used to elute TEV resistant material remaining on the resin.
Untagged protein eluted with TEV protease was run on a LabChip GX II Microfluidic system to analyze the mayor protein species present. 
Samples of total cell lysate, soluble cell lysate and Nickel Buffer B elution were run on a SDS-PAGE for analysis. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

For each target, the selected construct sequence was subcloned from the selected DNA plasmid.
Expression testing performed by QB3 MacroLab.

All genes were cloned into the 2BT10 plasmid, an AMP resistant ColE1 plasmid with a T7 promoter.
Each kinase domain was tagged with a N-terminal His10-TEV and co-expressed with either YopH (for Tyr kinases) or lambda phosphatase (for Ser/Thr kinases). 
Single colonies of transformants were cultivated with 900 $\mu$L of MagicMedia into a gas permeable sealed 96-well block. 
The cultures were incubated at 37 C for 4 hours and then at 16 C for 40 hours while shacking. 
Next, cells were centrifuged and the pellets were frozen at -80 C overnight. 
Cells were lysed on a rotating platform at room temperature for an hour using 700 $\mu$L of Solulyse (Genlantis) supplemented with 400 mM NaCl, 20 mM imidazole and protease inhibitors. 
For protein purification, 500 $\mu$L of the soluble lysate was added to a 25 $\mu$L Ni-NTA resin in a 96-well filter plate. 
Nickel Buffer A (25 mM HEPES pH 7.5, 5\% glycerol, 400 mM NaCl, 20 mM imidazole, 1 mM BME) was added and the plate was mixed for 30 minutes at room temperature. 
The resin was washed with 2 mL of Nickel Buffer A. 
Target proteins were eluted by a 2 hour incubation at room temperature with 10 $\mu$g of TEV protease in 80 $\mu$L of Nickel Buffer A.
A subsequent wash with 40 $\mu$L of Nickel Buffer A was performed to release more target protein. 
Nickel Buffer B (25 mM HEPES pH 7.5, 5\% glycerol, 400 mM NaCl, 400 mM imidazole, 1 mM BME) was used to elute TEV resistant material remaining on the resin.
Untagged protein eluted with TEV protease was run on a LabChip GX II Microfluidic system to analyze the mayor protein species present. 
Samples of total cell lysate, soluble cell lysate and Nickel Buffer B elution were run on a SDS-PAGE for analysis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RESULTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{section:results}

\subsection{PDBs mining results}

\subsection{Small-scale kinase expression test in E. coli}

A panel containing the 96 kinase domain constructs selected through our semi-automated method, was tested for expression in E. coli. 
From this initial test, 68 kinase domains expressed successfully (yield of more than 2 ng/$\mu$L ).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
